---
title: "GOplot"
author: "tobiasst"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  html_document:
    df_print: paged
    code_folding: hide
---


http://wencke.github.io

```{r init, message=F, warning=F}
library(SummarizedExperiment)
library(GOplot)
library(GOstats)
library(org.Hs.eg.db)
library(parallel)
```

## GO enrichment calculation and data preparation

Plotting shown for the combined (up and down-regulated genes) enrichments calculated using GOstats.
Package examples are using DAVID output in a specific format that I reconstructed from GOstats output

```{r}
go.all <- readRDS("gstats_all.rds")
res <- readRDS("res_HD_NSC_v_C116_NSC.rds")
se <- readRDS("se.rds")
res$entrez <- rowData(se)$entrez
res$symbol <- rowData(se)$symbol

flt <- !is.na(res$padj) & res$padj<0.1
adjp <- p.adjust(summary(go.all)$Pvalue)
df <- cbind(summary(go.all), adjp)

## reconstruct a "david" structure this will take a long time if list is long
pre <- mclapply(1:nrow(df), function(i) {
#for (i in 1:nrow(summary(go.all))) {
  go <-  summary(go.all)$GOBPID[i]
  ids <- unlist(mget(go,org.Hs.egGO2ALLEGS))
  genes <- res$symbol[res$entrez %in% ids & flt ]
	data.frame(Category="BP",
	           ID=go,Term=summary(go.all)$Term[i],
	           Genes=paste(genes, collapse=", "), 
	           adj_pval=adjp[i])
})

david <- Reduce(rbind, pre)

genelist <- data.frame(ID=res$symbol, logFC=res$log2FoldChange, AveExpr=log2(res$baseMean), t=res$stat, P.Value=res$pvalue, adj.P.Value=res$padj)[flt,]
circ <- circle_dat(david, genelist )
```

## The modified barplot (GOBar)

```{r, fig.width=8, fig.height=6}

# Generate a simple barplot
GOBar(subset(circ, category='BP'))
```

## The bubble plot (GOBubble)

```{r, fig.width=10, fig.height=8}
# Generate the bubble plot with a label threshold of 3
GOBubble(circ, labels = 3)
```

## Circular visualization of the results of gene- annotation enrichment analysis (GOCircle)

```{r, fig.width=10, fig.height=8}
GOCircle(circ)
```




```{r}
sessionInfo()
```

